Sequential algorithms to split and merge terabyte-scale 3D images

### 2017-06-20 paper.tex
Updates in cluster reads following discussion with @ValHayot (still work in progress)

The number of seeks performed by cluster reads depends on how blocks
loaded in memory arrange in the reconstructed image. In the best case,
complete contiguous slices of the reconstructed image can be assembled
in memory and written without seeking at all. In the worst case, some
rows in the reconstructed image are not covered by blocks loaded in
memory: $d^2$ seeks are then required, one for every partial row in
every partial slice. In the intermediary case, rows are complete but
some slices can only be partially reconstructed: $d$ seeks are then
required. See also Figure~\ref{fig:cluster-reads}. In summary:
\begin{equation}
  N_\mathrm{cluster\_reads}= n + \ceil*{\frac{bR}{m}}f(m,n,R)
\end{equation}
where:
\begin{equation}
  f(m,n,R)=
  \begin{cases}
    d^2 & $if there is an incomplete row$\\
    d   & $if there is an incomplete slice$\\
        & $but not incomplete row$\\
    1   & $otherwise$
\end{cases}
\end{equation}
\begin{figure}
\centering
\def\svgwidth{0.3\columnwidth}
\input{figures/no-seek.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/d-seeks.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/d2-seeks.pdf_tex}
\caption{Left: complete slices and rows are reconstructed in memory:
  no seeking is required. Center: complete rows but incomplete slices
  are reconstructed: $d$ seeks are required. Right: incomplete rows
  are reconstructed: $d^2$ seeks are required.}
\label{fig:cluster-reads}
\end{figure}

>>>>

The number of seeks performed by cluster reads depends on how blocks
loaded in memory arrange in the reconstructed image. In the best case,
complete contiguous slices of the reconstructed image can be assembled
in memory and written without seeking at all. In the worst case, some
rows in the reconstructed image are not covered by blocks loaded in
memory: $d^2$ seeks are then required, one for every partial row in
every partial slice. In the intermediary case, rows are complete but
some slices can only be partially reconstructed: $d$ seeks are then
required. See also Figure~\ref{fig:cluster-reads}. In summary:
\begin{equation}
  N_\mathrm{cluster\_reads}= n + \ceil*{\frac{bR}{m}}f(m,n,R)
\end{equation}
where:
\begin{equation}
  f(m,n,R)=
  \begin{cases}
    d^2 & $if there is an incomplete row$\\
    d   & $if there is an incomplete slice$\\
        & $but not incomplete row$\\
    1   & $otherwise$
\end{cases}
\end{equation}
\begin{figure}
\centering
\def\svgwidth{0.3\columnwidth}
\input{figures/case1.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case2.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case3-a.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case3-b.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case4.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case5.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case6-a.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case6-b.pdf_tex}
\def\svgwidth{0.3\columnwidth}
\input{figures/case7.pdf_tex}

\caption{Cluster reads configurations leading to different number of
  seeks.}
\label{fig:cluster-reads}
% See source files in
% https://drive.google.com/drive/folders/0BzT7pbvPDUdQRXppVlhfdS0ycGc?usp=sharing
\end{figure}
